\topskip 3.5truein
{
\baselineskip=10pt plus1pt minus1pt
\centerline{To my wife, Tonya,}
\centerline{and my parents,}
\centerline{for their love,}
\centerline{support, and}
\centerline{understanding.}
}
\vfill
\eject

\topskip 2truein
{\baselineskip 14pt
\line{\hskip 2truein\llap{``}If I have seen further it is by\hfill}
\line{\hskip 2truein{standing on the shoulders of giants''\hfill}}
}
\line{\hskip 3truein{Sir Isaac Newton\hfill}}
\vfill
\eject

\chapterhead{Acknowledgements}

I gratefully acknowledge the assistance and encouragement I have received from
my family, friends, colleagues, and instructors.  I am most especially thankful
to my advisor, James W. York, Jr., for his support, inspiration, and for many
invaluable discussions.  I have also benefitted greatly from my interactions
with Bernard Whiting, Charles Evans, Steve Christensen, Tsvi Piran, and Steve
Detweiler.  In particular, I wish to thank Bernard Whiting for his seemingly
endless patience and enthusiasm.

I am grateful for the support I have received from the Department of Physics and
Astronomy at The University of North Carolina at Chapel Hill.  Much of the
computational work contained in this dissertation has been performed on the
Convex supercomputer run by the Academic Computing Services at UNC--Chapel Hill
and  on the Cray Y-MP supercomputer at the North Carolina Supercomputing
Center.  Financial support has been provided in part through National Science
Foundation grants PHY-8407492, PHY-8908741, and PHY-9001645.

\vfill
\eject