\chapterhead{Appendix~C:  Numerical Solutions of the Two-Hole\cr Hamiltonian
Constraint in Bispherical Coordinates}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
This appendix contains the most important details from the numerical solution
of the two-hole Hamiltonian constraint described in Chapter~9.  The difference
equations for this approach were solved by Newton's method for systems of
equations and each linearized equation for the iterative correction was solved
directly by means of the LINPACK routines for factoring (DGBFA) and solving
(DGBSL) general banded matrices.  The solution for each configuration was
obtained at three different mesh resolutions.  The coarsest discretization
consisted of a mesh of $(80\times80)$ zones.  The intermediate discretization
consisted of a mesh of $(120\times120)$ zones.  The finest discretization
consisted of a mesh of $(160\times160)$ zones.  It was possible, though not
practicle, to use a discretization of $(200\times200)$ zones.  One set of runs
was obtained for configurations with $\beta=3$ to see if the results were
significantly better.  They were not, and the results of this run are not
included in this appendix.  (They are, however, included in the Richardson
extrapolated data used to construct Figures 14.1 through~14.7.)

The 60 tables which follow can be considered as ten groups of six tables.  Each
group of six tables corresponds to the six cases described in Chapter~14.  The
ten groups of six tables represent ten values of the separation parameter
$\beta=3\to12$.  Finally, each table lists results from the numerical
computations for the scaled total energy $E/a_1$, the scaled minimal surface
mass $M/a_1$, and the scaled proper separation $L/a_1$ as the linear or angular
momentum parameter is varied.  For each of the physical quantities listed in
each table, the value for each of the three mesh resolutions is listed along
with the  average Richardson extrapolated value $\Re$ obtaind by assuming the
error scales as first order in the mesh spacing.

\vfill
\eject

\input Tables/2-Hole.bs/bs3
\input Tables/2-Hole.bs/bs4
\input Tables/2-Hole.bs/bs5
\input Tables/2-Hole.bs/bs6
\input Tables/2-Hole.bs/bs7
\input Tables/2-Hole.bs/bs8
\input Tables/2-Hole.bs/bs9
\input Tables/2-Hole.bs/bs10
\input Tables/2-Hole.bs/bs11
\input Tables/2-Hole.bs/bs12
