\chapterhead{References}
%%%%%%%%%%%%%%%%%%%%%%%
\reference{Abrahams, A. M., [1990], Private Communication.}

\reference{Abrahams, A. M., and Evans, C. R., [1988], ``Reading off
gravitational radiation waveforms in numerical relativity calculations: 
Mathching to linearized gravity,'' {\it Phys. Rev.~D}, {\bf 37}, pp.~318--332.}

\reference{Abrahams, A. M., and Evans, C. R., [1990], ``Gauge invariant
treatment of gravitational radiation near the source:  Analysis and numerical
simulations,'' submitted to {\it Phys. Rev.~D}.}

\reference{Adler, S. L., and Piran, T., [1984], ``Relaxation methods for gauge
field equilibrium equations,'' {\it Rev. Mod. Phys.}, {\bf 56}, pp.~1--40.}

\reference{Allen, D. N. de G., [1954], {\it Relaxation Methods}, McGraw-Hill, New
York.}

\reference{Ames, W. F., [1977], {\it Numerical Methods for Partial Differential
Equations}, Academic Press, New York.}

\reference{Arnowitt, R., Desser, S., and Misner, C. W., [1962], ``The dynamics of
general relativity,'' in Witten [1962], pp.~227--265.}

\reference{Bergman, S. and Schiffer, M., [1953], {\it Kernel Functions and
Elliptic Differential Equations in Mathematical Physics}, Academic Press, New
York.}

\reference{Bernstein, D. H., and Hobill, D. W., [1990] Private Communication.}

\reference{Bishop, N. T., [1982], ``The closed trapped region and the apparent
horizon of two Schwarzschild black holes,'' {\it Gen. Rel. and Grav.}, {\bf 14},
pp.~717--723.}

\reference{Bishop, N. T., [1984], ``The horizons of two Schwarzschild black
holes,'' {\it Gen. Rel. and Grav.}, {\bf 16}, pp.~589--593.}

\reference{Bishop, N. T., [1988], ``The event horizons of two Schwarzschild black
holes,'' {\it Gen. Rel. and Grav.}, {\bf 20}, pp.~573--581.}

\reference{Bowen, J., [1979a], ``General form for the longitudinal momentum of a
spherically symmetric source,'' {\it Gen. Rel. and Grav.}, {\bf 11},
pp.~227--231.}

\reference{Bowen, J., [1979b], {\it Initial Value Problem on Non-Euclidean
Topologies}, Ph.D. dissertation, University of North Carolina--Chapel Hill.}

\reference{Bowen, J., [1982], ``General solutions for flat-space longitudinal
momentum ,'' {\it Gen. Rel. and Grav.}, {\bf 14}, pp.~1183--1191.}

\reference{Bowen, J., Rauber, J., and York, J. W., Jr., [1984], ``Two black holes
with axisymmetric parallel spins:  Initial data,'' {\it Class. Quantum Grav.},
{\bf 1}, pp.~591--610.}

\reference{Bowen, J. M., and York, J. W., Jr., [1980], ``Time-asymmetric initial
data for black holes and black-hole collisions,'' {Phys. Rev.~D}, {\bf 21},
pp.~2047--2056.}

\reference{Brandt, A., [1977], ``Multi-level adaptive solutions to boundary-value
problems,'' {\it Math. of Comp.}, {\bf 31}, pp.~333--390.}

\reference{Brandt, A., [1982], ``Guide to multigrid development,'' in Hackbusch
and Trottenberg 1982, pp.~220--312.}

\reference{Brill, D. R., and Lindquist, R. W., [1963], ``Interaction energy in
geometrostatics,'' {\it Phys. Rev.}, {\bf 131}, pp.~471--476.}

\reference{\v{C}ade\v{z}, A.,[1971], {\it Colliding Black Holes}, Ph.D.
dissertation, University of North Carolina--Chapel Hill.}

\reference{\v{C}ade\v{z}, A.,[1974], ``Apparent horizons in the two-black-hole
problem,'' {\it Ann. Phys.}, {\bf 83}, pp.~449--457.}

\reference{Cantor, M., and Kulkarni, A. D., [1982], ``Physical distinctions
between normalized solutions of the two-body problem of general relativity,''
{\it Phys. Rev.~D}, {\bf 25}, pp.~2521--2526.}

\reference{Centrella, J. M., [1986], {\it Dynamical Spacetimes and Numerical
Relativity}, Cambridge University Press, London.}

\reference{Choptuik, M. W., [1982], {\it A Study of Numerical Techniques for the
Initial Value Problem of General Relativity}, Masters thesis, University of
British Columbia.}

\reference{Choptuik, M. W., and Unruh, W. G., [1986], ``An introduction to the
multi-grid method for numerical relativists,'' {\it Gen. Rel. and Grav.}, {\bf
18}, pp 813--843.}

\reference{Choquet-Bruhat, Y., and York, J. W., Jr., [1980], ``The Cauchy
problem,'' in Held 1980, pp.~99--172.}

\reference{Christodoulou, D., [1970], ``Reversible and irreversible
transformations in black-hole physics,'' {\it Phys. Rev. Letters}, {\bf 25},
pp.~1596--1597.}

\reference{Cook, G. B., [1989], ``The Multigrid Technique,'' in Evans, Finn, and
Hobill 1989, pp.~222--229.}

\reference{Cook, G. B., and York, J. W., Jr., [1990], ``Apparent horizons for
boosted or spinning black holes,'' {\it Phys. Rev.~D}, {\bf 41}, pp.~1077--1085.}

\reference{Damour, T., [1983], ``Gravitational radiation and the motion of
compact bodies,'' in Deruelle and Piran 1983, pp.~59--144.}

\reference{Damour, T., [1987], ``The problem of motion in Newtonian and
Einsteinian gravity,'' in Hawking and Israel 1987, pp.~128--198.}

\reference{Detweiler, S., [1989], ``Kepler's third law in general relativity,''
in Evans, Finn, and Hobill 1989, pp.~43--56.}

\reference{Detweiler, S., [1989], Private Communication.}

\reference{Deruelle, N., and Piran, T., [1983], {\it Gravitational Radiation},
North-Holland Publishing Company, Amsterdam.}

\reference{Einstein, A., and Rosen, N., [1935], ``The particle problem in the
general theory of relativity,'' {\it Phys. Rev.}, {\bf 48}, pp.~73--77.}

\reference{Eppley, K., [1977], ``Evolution of time-symmetric gravitational
waves:  Initial data and apparent horizons,'' {\it Phys. Rev.~D}, {\bf 16},
pp.~1609--1614.}

\reference{Evans, C. R., [1984], {\it A Method for Numerical Relativity: 
Simulation of Axisymmetric Gravitational Collapse and Gravitational Radiation
Generation}, Ph.D. dissertation, University of Texas at Austin.}

\reference{Evans, C. R., [1986a], ``An approach for calculating axisymmetric
gravitational collapse,'' in Centrella 1986, pp.~3--39.}

\reference{Evans, C. R., [1986b], Unpublished work.}

\reference{Evans, C. R., [1987], ``Gravitational radiation from collisions of
compact stars,'' in Ulmer 1987, pp.~152--156.}

\reference{Evans, C. R., [1989], Private Communication.}

\reference{Evans, C. R., Finn, L. S., and Hobill, D. W., [1989], {\it Frontiers
in Numerical Relativity},  Cambridge University Press, London.}

\reference{Ferrell, R. C., and Eardley, D. M., [1989], ``Slowly moving maximally
charged black holes,'' in Evans, Finn, and Hobill 1989, pp.~27--42.}

\reference{Gibbons, G. W., [1972], ``The time symmetric initial value problem for
black holes,'' {\it Commun. Math. Phys.}, {\bf 27}, pp.~87--102.}

\reference{Gibbons, G. W., and Schutz, B. F., [1972], ``Limits on gravitational
radiation from two gravitationally bound black holes,'' {\it Mon. Not. R. Astr.
Soc.}, {\bf 159}, pp.~41P--45P.}

\reference{Hackbusch, W., and Trottenberg, U., [1982], {\it Multigrid Methods},
Springer-Verlag, Berlin.}

\reference{Hackbusch, W., [1985], {\it Multi-Grid Methods and Applications},
Springer-Verlag,\hfil\break Berlin.}

\reference{Hahn, S., and Lindquist, R., [1964], ``The two body problem in
geometrodynamics,'' {\it Ann. Phys.}, {\bf 29}, pp.~304--331.}

\reference{Hawking, S. W., [1971], ``Gravitational radiation from colliding black
holes,'' {\it Phys. Rev. Letters}, {\bf 26}, pp.~1344--1346.}

\reference{Hawking, S. W., and Ellis, G. F. R., [1973], {\it The Large Scale
Structure of Space-Time}, Cambridge University Press, London.}

\reference{Hawking, S. W., and Israel, W., [1987], {\it 300 Years of
Gravitation}, Cambridge University Press, London.}

\reference{Held, A., [1980], {\it General Relativity and Gravitation:  One
Hundred Years After the Birth of Albert Einstein}, Volume 1, Plenum Press,
London.}

\reference{Jaffe, J., [1975], ``The gravitational spin-spin force,'' {\it Gen.
Rel. and Grav.}, {\bf 6}, pp.~49--53.}

\reference{Kulkarni, A. D., [1984], ``Time-asymmetric initial data for the N
black hole problem in general relativity,'' {\it J. Math. Phys.}, {\bf 25},
pp.~1028--1034.}

\reference{Kulkarni, A. D., Shepley, L. C., and York, J. W., Jr., [1983],
``Initial data for $N$ black holes,'' {\it Phys. Lett.}, {\bf 96A},
pp.~228--230.}

\reference{Lindquist, R. W., [1963], ``Initial-value problems on Einstein-Rosen
manifolds,'' {\it J. Math. Phys.}, {\bf 4}, pp.~938--950.}

\reference{Mashoon, B., [1971], ``Particles with spin in a gravitational field,''
{\it J. Math. Phys.}, {\bf 12}, pp.~1075--1077.}

\reference{Matzner, R. and Shepley, L., [1982], {\it Spacetime and Geometry:  The
Alfred Schild Lectures}, University of Texas Press, Austin.}

\reference{Misner, C. W., [1963], ``The method of images in geometrostatics,''
{\it Ann. Phys.}, {\bf 24}, pp.~102--117.}

\reference{Misner, C. W., Thorne, K. S., and Wheeler, J. A., [1973], {\it
Gravitation}, W. H. Freeman and Company, New York.}

\reference{Mitchell, A. R., and Griffiths, D. F., [1980], {\it The Finite
Difference Method in Partial Differential Equations}, John Wiley and Sons, New
York.}

\reference{Moon, P., and Spencer, D. E., [1988], {\it Field Theory Handbook},
Springer-Verlag, Berlin.}

\reference{Nakamura, T., Kojima, Y., and Oohara, K., [1984], ``A method of
determining apparent horizons in three-dimensional numerical relativity,'' {\it
Phys. Lett.}, {\bf 106A}, pp.~235--238.}

\reference{Nakamura, T., Kojima, Y., and Oohara, K., [1985], ``Apparent horizons
of time-symmetric initial value for three black holes,'' {\it Phys. Lett.}, {\bf
107A}, pp.~452--455.}

\reference{Nakamura, T., and Oohara, K., [1989], ``Methods in 3D numerical
Relativity,'' in Evans, Finn, and Hobill 1989, pp.~254--280.}

\reference{\'{O} Murchada, N., and York, J. W., Jr., [1973], ``Existence and
uniqueness of solutions of the Hamiltonian constraint of general relativity on
compact manifolds,'' {\it J. Math. Phys.},  {\bf 14}, pp.~1551--1557.}

\reference{\'{O} Murchada, N., and York, J. W., Jr., [1974a], ``Initial-value
problem of general relativity.  I.  General formulation and physical
interpretation,'' {\it Phys. Rev.~D},  {\bf 10}, pp.~428--436.}

\reference{\'{O} Murchada, N., and York, J. W., Jr., [1974b], ``Initial-value
problem of general relativity.  II.  Stability of solution of the initial-value
equations,'' {\it Phys. Rev.~D},  {\bf 10}, pp.~437--446.}

\reference{\'{O} Murchada, N., and York, J. W., Jr., [1974c], ``Gravitational
energy,'' {\it Phys. Rev.~D},  {\bf 10}, pp.~2345--2357.}

\reference{\'{O} Murchada, N., and York, J. W., Jr., [1976a], ``Gravitational
momentum,'' unpublished.}

\reference{\'{O} Murchada, N., and York, J. W., Jr., [1976b], ``Gravitational
potentials:  A constructive approach to general relativity,'' {\it Gen. Rel. and
Grav.}, {\bf 7}, pp.~257--261.}

\reference{Papagiannis, M. D., [1977], {\it Eighth Texas Symposium on
Relativistic Astrophysics}, The New York Academy of Sciences, New York.}

\reference{Piran, T., [1988], Private Communication.}

\reference{Piran, T., [1989], Private Communication.}

\reference{Press, W. H., Flannery, B. P., Teukolky, S. A., and Vetterling, W.
T., [1988], {\it Numerical Recipes in C}, Cambridge University Press, London.}

\reference{Rauber, J. D., [1985], {\it Initial Data for Black Hole Collisions},
Ph.D. dissertation, University of North Carolina--Chapel Hill.}

\reference{Rauber, J. D., [1986], ``Initial data for black hole collisions,'' in
Centrella 1986, pp.~304--327.}

\reference{Smarr, L. L., \v{C}ade\v{z}, A., DeWitt, W., Eppley, K., [1976],
``Collision of two black holes:  Theoretical framework,'' {\it Phys. Rev.~D},
{\bf 14}, pp.~2443--2452.}

\reference{Smarr, L. L., [1977], ``Space-times generated by computers:  black
holes with gravitational radiation'', in Papagiannis 1977, pp.~569--604.}

\reference{Smarr, L. L., [1979], Sources of Gravitational Radiation, Cambridge
University Press, London.}

\reference{Smarr, L. L., and York, J. W., Jr., [1078a], ``Radiation gauge in
general relativity,'' {\it Phys. Rev.~D}, {\bf 17}, pp.~1945--1956.}

\reference{Smarr, L. L., and York, J. W., Jr., [1078b], ``Kinematical conditions
in the construction of spacetime,'' {\it Phys. Rev.~D}, {\bf 17},
pp.~2529--2551.}

\reference{Thornburg, J., [1987], ``Coordinates and boundary conditions for the
general relativistic initial data problem,'' {\it Class. Quantum Grav.}, {\bf 4},
pp.~1119--11131.}

\reference{Thorne, K. S., [1987], ``Gravitational radiation,'' in Hawking and
Israel 1987, pp. 330--458.}

\reference{Tipler, F. J., [1980], {\it Essays in General Relativity}, Academic
Press, New York.}

\reference{Tomimatsu, A., [1989], ``Gravitational field in a collision of two
Schwarzschild black holes,'' Preprint.}

\reference{Ulmer, M. P., [1987], {\it Proceedings of the 13th Texas Symposium on
Relativistic Astrophysics}, World Scientific Publishing, Singapore.}

\reference{Wald, R. M., [1972], ``Gravitational spin interaction,'' {\it Phys.
Rev.~D}, {\bf 6}, pp.~406--413.}

\reference{Wald, R. M., [1984], {\it General Relativity}, The University of
Chicago Press, Chicago.}

\reference{Weinberg, S., [1972], {\it Gravitation and Cosmology:  Principles and
Applications of the General Theory of Relativity}, Wiley and Sons, New York.}

\reference{Witten, L., [1962], {\it Gravitation:  An Introduction to Current
Research}, John Wiley and Sons, New York.}

\reference{York, J. W., Jr., [1971], ``Gravitational degrees of freedom and the
initial-value problem,'' {\it Phys. Rev. Letters}, {\bf 26}, pp.~1656--1658.}

\reference{York, J. W., Jr., [1972], ``Role of conformal three-geometry in the
dynamics of gravitation,'' {\it Phys. Rev. Letters}, {\bf 28}, pp.~1082--1085.}

\reference{York, J. W., Jr. [1973a], ``Conformally invariant orthogonal
decomposition of symmetric tensors on Riemannian manifolds and the initial-value
problem of general relativity,'' {\it J. Math. Phys.}, {\bf 14}, pp.~456--464.}

\reference{York, J. W., Jr. [1973b], ``Initial-value problem and dynamics of
general relativity,'' Lecture notes, Princeton University.}

\reference{York, J. W., Jr. [1974], ``Covariant decompositions of symmetric
tensors in the theory of gravitation,'' {\it Ann. Inst. Henri Poincar\'{e}},
{\bf 21}, pp.~319--332.}

\reference{York, J. W., Jr., [1979], ``Kinematics and Dynamics of General
Relativity,'' in Smarr 1979, pp.~83--126.}

\reference{York, J. W., Jr., [1980], ``Energy and momentum of the gravitational
field,'' in Tipler, pp.~39--58.}

\reference{York, J. W., Jr., [1984], ``Initial data for $N$ black holes,'' {\it
Physica}, {\bf 124A}, pp.~629--637.}

\reference{York, J. W., Jr., [1989], ``Initial data for collisions of black holes
and other gravitational miscellany,'' in Evans, Finn, and Hobill 1989,
pp.~89--109.}

\reference{York, J. W., Jr., and Piran, T., [1982], ``The initial value problem
and beyond,'' in Matzner and Shepley 1982, pp.~147--176.}

\vfill
\eject
